Block bootstrap consistency\\under weak assumptions

### 2016-06-08 Paper.tex
[#18] Add examples of heterogeneity allowed under assumption 2
This commit adds several paragraphs that explain the sort of hetergoeneity
in the means that Theorem 1's assumptions allow. This explanation is in
response to one of the referees on the paper.

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that De Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
accommodate larger block sizes.%
\footnote{Note that this is one reason that we are presenting our
  results using general triangular-array notation: to allow for the
  means to change over time for comparison with \citepos{GoW:02} and
  \citepos{GoJ:03} results.}

>>>>

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that De Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt.

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} when the expected block length is $o(\sqrt{n})$. When
the blocks are longer than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$,
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have defined $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the Stationary Bootstrap the same relationship must hold for the
expected block length. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that its timing could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

We can also use the same DGP to produce scenarios where
Theorem~\ref{T1}'s Assumption~2 is satisfied.  The first mimics a
setting where the break is estimated and the bootstrap is applied to
the post-break sample, but a small number of pre-break observations
are accidentally included in the data set as well. Here
$\Delta_n = \Delta_0$ and $T_n = T_0$ for some finite $T_0$. In this
case, Assumption 2 holds hold as long as $M_n = o(\sqrt{n})$.
Similarly, if the break is moderate with unknown timing in the sense
of \citet{ElM:07}, so $\Delta_n = \Delta / \sqrt{n}$ and
$T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
again holds as long as $M_n = o(\sqrt{n})$. Consequently, block sizes
of length $o(\sqrt{n})$ ensure that the conditions of
Theorem~\ref{T1}'s when there is a moderate amount of
heterogeneity---either because the sample is chosen to lie after a
large break estimated break or because any breaks are smaller in
magnitude and, consequently, potentially difficult to detect. When the
degree of heterogeneity is very small or nonexistent, so
$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
block lengths can also satisfy Assumption 2.
